Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-19 src/article.tex
Add MultiLabelMarginLoss bibl
Update RepBERT score function.
Update SparTerm L_rank function.

    \paragraph{Training the importance predictor.}
    There is a set of N training instances $R=\{(q_1, p_{1+}, p_{1-}), ..., (q_N, p_N+, p_N-)\}$,
    each of which contains a query $q_i$, a positive passage $p_{i+}$ and a negative one $p_i-$,
    such that the first passage is more relevant the query than the second one.
    As a result, the loss function has the following form:
    \begin{equation}
        L_{rank}(q_i,p_{i+},p_{i-}) = -log \frac
        {e^{sim(q_i',p_{i+}')}}
        {e^{sim(q_i',p_{i+}')} + e^{sim(q_i',p_{i-}')}}
    \end{equation}
    where $q_i',p_{i+}',p_{i-}'$ is the sparse representation of $q_i,p_{i+},p_{i-}$
    received by Equation (\ref{eqn:sparterm:mapping-process}), \emph{sim} represents a function
    to measure the similarity (e.g. dot product).

@@

    \begin{equation}
        Rel(query,doc) = Embed(query)^T \cdot Embed(doc)
    \end{equation}

    \paragraph{Training}
    During training, it is necessary to make a embeddings inner product for the relevant
    query-document pairs larger than for the irrelevant ones.
    The model uses the MultiLabelMarginLoss as loss function:
    \begin{multline}
        \mathnormal{L}(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-) = \\
        \frac{1}{n} \cdot \sum_{1 \leq i \leq m,m < j \leq n}
        max(0, 1 - (Rel(q,d_i^+) - Rel(q,d_j^-)))
    \end{multline}
    where $(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-)$ is one instance of the input training batch,
    \emph{q} is query, \emph{m} is quantity of relevant documents and \emph{n - m} is quantity
    of irrelevant documents\cite{RepBERT}.\\\par
    The model has a simple architecture in order to improve work efficiency.

>>>>

    \paragraph{Training the importance predictor.}
    There is a set of N training instances $R=\{(q_1, d_{1+}, d_{1-}), ..., (q_N, d_N+, d_N-)\}$,
    each of which contains a query $q_i$, a positive document (passage) $d_{i+}$ and a negative
    one $d_i-$, such that the first document is more relevant the query than the second one.
    As a result, the loss function has the following form:
    \begin{equation}
        L_{rank} = -log \frac
        {e^{s(q_i,d_{i+})}}
        {e^{s(q_i,d_{i+})} + e^{s(q_i,d_{i-})}}
    \end{equation}
    where $s(q,d)$ is denote the ranking score obtained via dot product between $d$ and $q$
    representations from Equation (\ref{eqn:sparterm:mapping-process}).

@@

    \begin{equation}
        s(q,d) = Embed(q)^T \cdot Embed(d)
    \end{equation}
    where $Embed(q)^T$ and $Embed(d)$ are $\phi(q)$ and $\psi(d)$ respectively.

    \paragraph{Training}
    During training, it is necessary to make a embeddings inner product for the relevant
    query-document pairs larger than for the irrelevant ones.
    The model uses the MultiLabelMarginLoss \cite{multiLabelMarginLoss} as loss function:
    \begin{multline}
        \mathnormal{L}(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-) = \\
        \frac{1}{n} \cdot \sum_{1 \leq i \leq m,m < j \leq n}
        max(0, 1 - (Rel(q,d_i^+) - Rel(q,d_j^-)))
    \end{multline}
    where $(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-)$ is one instance of the input training batch,
    \emph{q} is query, \emph{m} is quantity of relevant documents and \emph{n - m} is quantity
    of irrelevant documents\cite{RepBERT}.\\\par
    The model has a simple architecture in order to improve work efficiency.
